A Comparison of Graph Processing Systems

### 2020-08-14 documentation/paper/main.tex
giraph overview and input format
added measurement methods for times

\bibliography{literature.bib}
\title{Forschungsprojekt}
\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{()\\
@stud.uni-stuttgart.de}}
\date{\today}

@@

\begin{IEEEkeywords}
graphs, distributed computing, Galois, Ligra, Polymer, Giraph, Gluon
\end{IEEEkeywords}

@@

\section{Results}
\subsection{Komplexität Aufsetzen}
Systeme wie distr. Giraph bei denen man erstmal ewig suchen muss bis man überhaupt einen Guide findet sollten hier schlechter abschneiden. \emph{vorausgesetzt, wir nehmen das hier überhaupt mit auf..}

@@

\subsection{Ergebnisse exec time}
hier erhoffe ich mir einen Vergleich der Ladezeiten und erwarte, dass Systeme wie Giraph, die erstmal auf irgendwas warten schlecht abschneiden.
Aber vielleicht ist auch die setup time bei gleichen frameworks zwischen verteilt und shared memory ganz interessant zu vergleichen.

@@

Also we use Gluon~\cite{vertGalois} for the distributed setups.

@@

@@

Everything can be retrieved on our GitHub repository
\url{http://www.github.com/serengti/Forschungsprojekt}.

For each Framework, there is a

@@

>>>>

\bibliography{literature.bib}
\title{A Comparison of Graph Processing Systems}
\author{\IEEEauthorblockN{Simon König}
\IEEEauthorblockA{(3344789)\\
st156571@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Leon Matzner}
\IEEEauthorblockA{(3315161)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Felix Rollbühler}
\IEEEauthorblockA{(3310069)\\
@stud.uni-stuttgart.de}
\and
\IEEEauthorblockN{Jakob Schmid}
\IEEEauthorblockA{()\\
@stud.uni-stuttgart.de}}
\date{\today}

@@

\begin{IEEEkeywords}
graphs, distributed computing, Galois, Ligra, Polymer, Giraph, Gluon, Gemini
\end{IEEEkeywords}

@@

\section{Results}
\subsection{Komplexität Aufsetzen}
Systeme wie distr. Galois, bei denen man erstmal ewig suchen muss bis man überhaupt einen Guide findet sollten hier schlechter abschneiden. \emph{vorausgesetzt, wir nehmen das hier überhaupt mit auf..}

@@

\subsection{Ergebnisse exec time}

hier erhoffe ich mir einen Vergleich der Ladezeiten und erwarte, dass Systeme wie Giraph, die erstmal auf irgendwas warten schlecht abschneiden.
Aber vielleicht ist auch die setup time bei gleichen frameworks zwischen verteilt und shared memory ganz interessant zu vergleichen.

@@

Also we use Gluon~\cite{vertGalois} for the distributed Galois setups.

@@

%We would like to thank our supervisor Heiko Geppert for continued guidance and support.

@@

Our GitHub repository: \url{http://www.github.com/serengti/Forschungsprojekt}.

The graphs were downloaded from the graph database associated with the Koblenz Network Collection (KONECT)\cite{konect}.

@@

\bibitem{konect}
J.~Kunegis, ``Konect: the koblenz network collection,'' 05 2013, pp.
  1343--1350.

### 2020-08-14 documentation/paper/sections/testingMethods.tex
clean up
added measurement methods for times

%!TEX root=main.tex
\subsection{Hardware and Software}
For testing all systems we used 5 machines with 96 CPU cores each (48 physical) and 256 GB of RAM. One of those machines only had 128 GB of RAM, this one was only used as part of the calculation cluster for the distributed systems.
All servers were running Ubuntu 19.x.
Setup of each framework was performed according to our provided installation guides.

\subsection{Benchmark setup}
We measured the total runtime of each process as well as the actual calculation times. The console output of each frameworks was used as an indicator for when loading the graph data was finished. This proved to be more difficult than expected in some cases.

Each test case consisting of graph, framework and in some cases even the algorithm was run 10 times, allowing us to smooth slight variations in the measured times. This also helps to reduce the error we introduced by measuring time through the console log.

@@

We will compare both the computation times as well es the execution times. This way we compare how much setup time each framework has.

>>>>

%!TEX root=../main.tex

\subsection{Hardware and Software}
For testing all systems we used 5 machines with 96 CPU cores each (48 physical) and 256 GB of RAM. One of those machines was only used as part of the distributed cluster, since it only has 128 GB of RAM.
All servers were running Ubuntu 19.x.
Setup of each framework was performed according to our provided installation guides.

@@

The complete log files and extracted raw results will be available in our repository as well.

\subsection{Measurements}
For every framework, we measured the \emph{execution time} as the time from start to finish of the console command.

For the \emph{calculation time}, we tried to extract only the time the framework actually executed the algorithm. We came up with the following:
\begin{itemize}
	\item For Galois, we resulted to extracting console log time stamps. Galois outputs \texttt{Reading graph complete.}. Calculation time is the time from this output to the end of execution.
	\item Polymer outputs the name of the algorithm followed by a measured time.
	\item Gemini outputs a line \texttt{exec\_time=x}, which was used to measure the calculation time. 
	\item Ligra outputs a measured time with \texttt{Running time : x}.
	\item Giraph has built in timers for the iterations (supersteps) which we used to extract the computation time.
\end{itemize}
Each test case consisting of graph, framework and algorithm was run 10 times, allowing us to smooth slight variations in the measured times.
